Methods to prioritise pop-up active transport infrastructure

### 2020-05-09 article.Rmd
Update figure 2

```{r commonplace, fig.cap="Screenshot from the website [salfordliveablestreets.commonplace.is](https://salfordliveablestreets.commonplace.is/comments) to support community and local government level responses to the Covid-19 pandemic, including the prioritisation of pop-up active transport infrastructure." }
knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
```

@@

```{r preprocess}
# remove motorways
r_original$highway2 = r_original$highway
r_original$highway2 = gsub(pattern = "_link", replacement = "", r_original$highway)
highway_table = table(r_original$highway)
highway_rare = highway_table[highway_table < nrow(r_original) / 100]
highway_remove = names(highway_rare)[!grepl(pattern = "motor|living|ped", x = names(highway_rare))]
r_cleaned = r_original %>% 
  filter(!grepl(pattern = "motorway", x = highway)) %>% 
  mutate(highway2 = case_when(
  highway2 %in% highway_remove ~ "other",
  grepl(pattern = "path|track|trunk", highway2) ~ "other",
  grepl(pattern = "ped|liv", highway2) ~ "pedestrian/living_street",
  TRUE ~ highway2
  )) %>% 
  mutate(maxspeed = case_when(
    maxspeed <= 20 ~ "20 mph or less",
    maxspeed > 20 & maxspeed <= 30 ~ "30 mph",
    maxspeed > 40 & maxspeed <= 40 ~ "40 mph",
    maxspeed > 50 ~ "50+ mph",
  ))
rj = inner_join(r_cleaned, rtid)
cy = r_cleaned %>% filter(highway == "cycleway")
r_central = rj[city_centre_buffer, ]
r_main = r_central %>% 
  filter(grepl(pattern = "cycleway|primary|second|tert", highway2))
```

@@

Datasets from the PCT and CyIPT project were merged, resulting key variables summarised in Table 1.
A map showing the spatial distribution of hospitals in the case study city of Leeds, which is used for demonstrating the methods, is shown in Figure \@ref(fig:hospitals).

@@

```{r hospitals, fig.cap="Overview map of input data, showing the main highway types and location of hospitals in Leeds"}
m1 = tm_shape(r_main %>% mutate(`Highway type` = highway2)) +
  tm_lines(col = "Highway type", palette = c("green", "black", "blue", "grey")) +
  tm_shape(h_leeds) + tm_dots(size = 0.5, col = "ParentName", palette = "Dark2", title = "Hospital group") +
  tm_layout(legend.outside = TRUE)
# + tm_text("OrganisationName")
m1
```

>>>>

```{r commonplace, fig.cap="Screenshot from the website salfordliveablestreets.commonplace.is to support local responses to the Covid-19 pandemic, including the prioritisation of pop-up active transport infrastructure."}
knitr::include_graphics("https://user-images.githubusercontent.com/1825120/81451234-ed82d200-917b-11ea-977d-fff1665378c5.png")
```

@@

```{r preprocess}
# remove motorways
r_original$highway2 = r_original$highway
r_original$highway2 = gsub(pattern = "_link", replacement = "", r_original$highway)
highway_table = table(r_original$highway)
highway_rare = highway_table[highway_table < nrow(r_original) / 100]
highway_remove = names(highway_rare)[!grepl(pattern = "motor|living|ped", x = names(highway_rare))]
r_cleaned = r_original %>% 
  filter(!grepl(pattern = "motorway", x = highway)) %>% 
  mutate(highway2 = case_when(
  highway2 %in% highway_remove ~ "other",
  grepl(pattern = "path|track|trunk", highway2) ~ "other",
  grepl(pattern = "ped|liv", highway2) ~ "pedestrian/living_street",
  TRUE ~ highway2
  )) %>% 
  mutate(maxspeed = case_when(
    maxspeed <= 20 ~ "20 mph or less",
    maxspeed > 20 & maxspeed <= 30 ~ "30 mph",
    maxspeed > 40 & maxspeed <= 40 ~ "40 mph",
    maxspeed > 50 ~ "50+ mph",
  )) %>% 
  mutate(pctgov = as.numeric(pctgov))
rj = inner_join(r_cleaned, rtid)
cy = r_cleaned %>% filter(highway == "cycleway")
r_central = rj[city_centre_buffer, ]
r_main = r_central %>% 
  filter(grepl(pattern = "cycleway|primary|second|tert", highway2))
```

@@

Datasets from the PCT and CyIPT project were merged, resulting in key variables summarised in Table 1.
A map showing the spatial distribution of hospitals in the case study city of Leeds is shown in Figure \@ref(fig:hospitals).

@@

```{r hospitals, fig.cap="Overview map of input data, showing the main highway types and location of hospitals in Leeds"}
m1 = r_main %>%
  mutate(`Highway type` = highway2) %>% 
  mutate(`Cycling potential` = case_when(pctgov < 100 ~ 100, TRUE ~ pctgov)) %>% 
  tm_shape() +
  tm_lines(col = "Highway type", palette = c("green", "black", "blue", "grey"),
           lwd = "Cycling potential", scale = 5, lwd.legend = c(100, 200, 500, 1000),
           lwd.legend.labels = c("0 - 100", "100 - 200", "200 - 500", "500+")) +
  tm_shape(h_leeds) + tm_dots(size = 0.5, col = "ParentName", palette = "Dark2", title = "Hospital group") +
  tm_layout(legend.outside = TRUE)
# + tm_text("OrganisationName")
m1
```
